Environments and eval in R

### 2020-12-29 analysis/environments.Rmd
Environments and ggplot

env_calls <- eval_calls_absolute %>%
  extract(environment_class, regex = "((?:new\\+)*)caller-([[:digit:]]+)-(.*)", into = c("new_env", "hierarchy", "specific_env"), remove = FALSE, convert = TRUE) %>%
  mutate(new_env = na_if(new_env, ""), specific_env = na_if(specific_env, ""), new_env = str_count(new_env, fixed("new+"))) %>%
  mutate(specific_env = if_else(specific_env == "emptyR_EmptyEnv", "empty", specific_env))
```

>>>>

env_calls <- eval_calls_absolute %>% ungroup() %>%
  extract(environment_class, regex = "((?:new\\+)*)caller-([[:digit:]]+)-(.*)", into = c("new_env", "hierarchy", "specific_env"), remove = FALSE, convert = TRUE) %>%
  mutate(new_env = na_if(new_env, ""), specific_env = na_if(specific_env, ""), new_env = str_count(new_env, fixed("new+"))) %>%
  mutate(specific_env = if_else(specific_env == "emptyR_EmptyEnv", "empty", specific_env))
```

_ggplot2_ again is responsible for this `new.env` 4 times!

```{r}
env_calls %>% filter(!is.na(new_env), specific_env == "global") %>% count(new_env, wt = nb_ev_calls, sort = TRUE)

env_calls %>% filter(new_env == 4, specific_env == "global") %>% count(eval_source, wt = nb_ev_calls, sort = TRUE)
```
